IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-09-16 main.tex
:triangular_flag_on_post: arXiv and TCOM 210916

		\begin{subsection}{Active Beamforming}
			The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$. Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduces the size of variables from $2MN$ to $2(M+N)$. The weight on subband $n$ is essentially
			\begin{equation}\label{eq:w}
				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n},
			\end{equation}
			where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder. Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}_+^{N \times 1}$. The MRT precoder at subband $n$ is given by
			\begin{equation}\label{eq:b_n}
				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
			\end{equation}

@@

		\begin{subsection}{Low-Complexity Adaptive Design}
			To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in time and power domains, respectively. For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
			\begin{equation}\label{eq:wf}
				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+},
			\end{equation}
			where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here. On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
			\begin{equation}\label{eq:smf}
				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha,
			\end{equation}
			where the scaling ratio $\alpha \ge 1$ is predetermined to exploit the rectifier nonlinearity and frequency selectivity. When the receiver works in TS mode, there is no superposition in the suboptimal waveform design (modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session). When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
			\begin{align}
				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha, \label{eq:s_p}
			\end{align}
			where the combining ratio $\delta$ determines the priority of multisine waveform at the transmitter, and the splitting ratio $\rho$ determines the priority of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large. Heuristically, $\delta^{\star}$ and $\rho^{\star}$ should approximately equal at each point to boost the R-E tradeoff.}

>>>>

		\begin{subsection}{Active Beamforming}
			The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$. Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduce the size of variables from $2MN$ to $2(M+N)$. The weight on subband $n$ is essentially
			\begin{equation}\label{eq:w}
				\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n},
			\end{equation}
			where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder. Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}_+^{N \times 1}$. The MRT precoder at subband $n$ is given by
			\begin{equation}\label{eq:b_n}
				\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
			\end{equation}

@@

		\begin{subsection}{Low-Complexity Adaptive Design}
			To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in time and power domains, respectively. For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
			\begin{equation}\label{eq:wf}
				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+},
			\end{equation}
			where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here. On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
			\begin{equation}\label{eq:smf}
				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha,
			\end{equation}
			where the scaling ratio $\alpha \ge 1$ is predetermined to exploit the rectifier nonlinearity and frequency selectivity. When the receiver works in TS mode, there is no superposition in the suboptimal waveform design (modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session). When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
			\begin{align}
				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha, \label{eq:s_p}
			\end{align}
			where the $\delta$ determines the power ratio of multisine waveform at the transmitter, and $\rho$ determines the power ratio of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large. Intuitively, $\delta^{\star}$ and $\rho^{\star}$ should be positively correlated for efficient SWIPT design.}
